### 2022-06-12 paper.tex
added citation to SciPy

The function \texttt{scbs prepare} reads a set of methylation files (e.g. produced by Bismark) and produces a file that stores the matrix $x$ in a space-efficient format, as follows: $x$ is represented as a SciPy sparse matrix, encoding the actual values 0, 1, and NA as -1, 1, and 0, respectively. Coding NA (the most common value) as 0 leverages SciPy's sparse matrix storage. In all the follows here, any mention of $x$ will, however, always mean the encoding as $x_{ij}\in\{0,1,\text{NA}\}$.

>>>>

The function \texttt{scbs prepare} reads a set of methylation files (e.g. produced by Bismark) and produces a file that stores the matrix $x$ in a space-efficient format, as follows: $x$ is represented as a SciPy sparse matrix \citep{SciPy}, encoding the actual values 0, 1, and NA as -1, 1, and 0, respectively. Coding NA (the most common value) as 0 leverages SciPy's sparse matrix storage. In all the follows here, any mention of $x$ will, however, always mean the encoding as $x_{ij}\in\{0,1,\text{NA}\}$.
